A note on multi agent learning

### 2016-06-16 multiAgentLearning/paper/article.tex
Title and added a place for each paper

\abstract{
	%TODO abstract
}

%TODO Intro blurb, if any

@@

Such assumptions can include:

@@

The Nash equilibrium of this games lies on Defect,Defect. However, all but
defect are pareto optimal actions.

\section{References to treat}
\begin{itemize}
  \item \citep{stimpson:2001}
  \item \citep{stimpson:2003}
  \item \citep{sandholm} % q-learning in iterated prisoners dilemma
  \item \citep{arthur} % maybe not, comparing algorithms against humans
  \item \citep{bowling}
  \item \citep{feltovich}
  \item \citep{crandall}
\end{itemize}

>>>>

\abstract{
  %TODO abstract
	abstract..
}

@@

@@

The Nash equilibrium of this games lies on Defect,Defect. However, all but
that action are pareto optimal actions.

\section{Properties of satisifing play}
Using both \citep{karandikar} and \citep{stimpson:2001} works to look deeper
at the properties of satisifing play.

karandikar used a theoretical proofing method, wehreas stimpson showed some
experimental results.

also showing the contrast graph which supports the work of \citep{arthur}

\section{An extended satisficing play}

In here we discuss the work of \citep{stimpson:2003}, where he extends the
algorithm to be played with mutliple action choices.

\section{Satisficing compared to other learning methods}
With help of the work of \citep{crandall} saticificing play is compared
to Q-learning and WOLF-PHC.
Q-learning is explained briefly with help of \citep{sandholm} and WOLF-PHC
with help of \citep{bowling}.

Finally some graphs are shown how they compare
